\newcommand{\finalCompanyName}{Aarhus Kommune}
\newcommand{\finalJobtitle}{Data Scientist}
\newcommand{\finalIntroduction}{I am excited to apply for the Data Scientist position at Aarhus Kommune. My passion for IT and AI, particularly in developing and evaluating machine learning models, aligns seamlessly with the role's focus on natural language processing (NLP).}
\newcommand{\finalMotivation}{My motivation to join Aarhus Kommune arises from my deep interest in AI and machine learning, particularly in NLP. My academic background has equipped me with the skills to develop, train, and evaluate machine learning models. I am particularly driven by the opportunity to work on projects that support various departments within the municipality, ensuring that AI technologies are effectively integrated to improve public services. My experience in project management has refined my ability to work collaboratively with diverse teams, ensuring that project goals are met efficiently. I am eager to bring my skills in data science and machine learning to Aarhus Kommune, contributing to innovative solutions that address real world challenges. The dynamic work environment and opportunities for professional growth at Aarhus Kommune are highly appealing, and I am excited about the prospect of contributing to your team.}
\newcommand{\finalSkills}{My skills in business analytics, strategy, and both non technical and technical communication will be invaluable in translating complex data insights into actionable strategies for Aarhus Kommune. My proficiency in Python, SQL, and various machine learning frameworks like TensorFlow and PyTorch will enable me to develop robust AI models. Additionally, my experience with Agile development and SCRUM methodologies will ensure that projects are managed efficiently and delivered on time. These skills will help Aarhus Kommune leverage data to improve public services and drive innovation.}
\newcommand{\finalEducationMaster}{In the summer of 2023, I completed my Master's degree in Data Science ICT. My thesis utilized foundational transformer models to semi automatically generate PEST analyses, which were improved with Named Entity Recognition and summarization techniques. This project involved analyzing publicly available data to provide macroeconomic insights, particularly concerning market expansion. The objective was to synthesize summaries from vectorized unstructured data, retrieving information based on semantic similarity and ranking through general purpose language models.}
\newcommand{\finalEducationBachelor}{Additionally, I hold a Professional Bachelor's Degree in Economics and IT. For my bachelor's thesis, I developed an enterprise architecture strategy for EnviroProcess Denmark and its parent company, EnviroProcess AB. This strategy was designed to align IT initiatives with the subsidiary’s core competencies, specific service knowledge, unique industry insights, and overall project execution.}
\newcommand{\finalContinuedLearning}{I am committed to continuously enhancing my skills and am currently exploring areas such as knowledge engineering, decision intelligence, and multi agent learning frameworks. I am willing to learn what is necessary for the company and specific role.}
\newcommand{\finalThankYou}{Thank you for your time. I look forward to the chance to discuss how my background and ambitions align with the goals of Aarhus Kommune. I am enthusiastic about potentially contributing to your projects and would appreciate the opportunity to discuss this further over a coffee.}
