\newcommand{\finalCompanyName}{Vestas}
\newcommand{\finalJobtitle}{Data Engineer}
\newcommand{\finalIntroduction}{I am excited to apply for the Data Engineer position at Vestas. My interest in IT and AI, combined with my academic background, aligns seamlessly with the role's requirements. I am eager to contribute to designing, constructing, and maintaining scalable, reliable, and efficient data products.}
\newcommand{\finalMotivation}{I am motivated by the opportunity to work with cutting edge cloud technologies such as Snowflake, Databricks, dbt, and Azure Services. My academic experience in project management and data engineering has equipped me with comprehensive analytical and problem solving skills, which I am eager to apply at Vestas. I am particularly drawn to the role's emphasis on managing and monitoring data products, collaborating with stakeholders, and establishing necessary integrations for data extraction. My proficiency in SQL and Python, along with my experience in supervised and unsupervised learning, will enable me to contribute effectively to your team. I am excited about the prospect of working in an environment that values continuous learning and innovation. I am confident that my background and skills will allow me to add value to Vestas by developing robust data solutions that drive business success.}
\newcommand{\finalSkills}{My skills include business analytics, strategy, and both non technical and technical communication. I have a working understanding of Python, SQL, and R, and I am proficient in tools like Docker, TensorFlow2, and FastAPI. I am detail oriented, a creative thinker, and a problem solver. These skills will enable me to design and maintain efficient data products, collaborate effectively with stakeholders, and ensure that data solutions align with Vestas' business goals.}
\newcommand{\finalEducationMaster}{In the summer of 2023, I completed my Master's degree in Data Science ICT. My thesis utilized foundational transformer models to semi automatically generate PEST analyses, which were improved with Named Entity Recognition and summarization techniques. This project involved analyzing publicly available data to provide macroeconomic insights, particularly concerning market expansion. The objective was to synthesize summaries from vectorized unstructured data, retrieving information based on semantic similarity and ranking through general purpose language models.}
\newcommand{\finalEducationBachelor}{Additionally, I hold a Professional Bachelor's Degree in Economics and IT. For my bachelor's thesis, I developed an enterprise architecture strategy for EnviroProcess Denmark and its parent company, EnviroProcess AB. This strategy was designed to align IT initiatives with the subsidiary’s core competencies, specific service knowledge, unique industry insights, and overall project execution.}
\newcommand{\finalContinuedLearning}{I am committed to continuously enhancing my skills and am currently exploring areas such as knowledge engineering, decision intelligence, and multi agent learning frameworks. Additionally, I am open to learning what is necessary for the company and specific role.}
\newcommand{\finalThankYou}{Thank you for your time. I look forward to the chance to discuss how my background and ambitions align with the goals of Vestas. I am enthusiastic about potentially contributing to your projects and would appreciate the opportunity to discuss this further over a coffee.}
