\newcommand{\finalCompanyName}{Aarhus Kommune}
\newcommand{\finalJobtitle}{Data Scientist}
\newcommand{\finalIntroduction}{I am excited about the opportunity to join Aarhus Kommune as a Data Scientist. My interest lies in IT and AI, particularly in exploring data, developing, training, and evaluating machine learning models with a focus on NLP.}
\newcommand{\finalMotivation}{I am driven by a passion for AI and IT, particularly in the field of natural language processing. My academic background has equipped me with the skills to explore data, develop, train, and evaluate machine learning models. I believe that my knowledge in algorithms, data structures, and software engineering can be highly beneficial for Aarhus Kommune. For instance, my experience with Python and SQL can be utilized to develop robust data pipelines, while my understanding of NLP can aid in the development of a new Danish language model. Additionally, my skills in business analytics and strategy can help align AI initiatives with the broader goals of the organization. I am eager to work closely with colleagues across various departments to implement AI technologies and support the development of innovative solutions. My adaptability and problem solving abilities make me a strong candidate for this role, and I am excited about the prospect of contributing to a dynamic work environment that offers opportunities for professional growth.}
\newcommand{\finalSkills}{My skill set includes a strong foundation in business analytics, strategy, and both non technical and technical communication. I am proficient in Python, SQL, and R, which are essential for data analysis and machine learning tasks. My experience with frameworks like TensorFlow and PyTorch allows me to build and evaluate complex models. Additionally, my project management skills, including familiarity with Agile development and SCRUM, enable me to effectively lead and collaborate on projects. These skills can be utilized to streamline processes, enhance data driven decision making, and develop innovative AI solutions for Aarhus Kommune.}
\newcommand{\finalEducationMaster}{In the summer of 2023, I completed my Master's degree in Data Science ICT. My thesis utilized foundational transformer models to semi automatically generate PEST analyses, which were improved with Named Entity Recognition and summarization techniques. This project involved analyzing publicly available data to provide macroeconomic insights, particularly concerning market expansion. The objective was to synthesize summaries from vectorized unstructured data, retrieving information based on semantic similarity and ranking through general purpose language models.}
\newcommand{\finalEducationBachelor}{Additionally, I hold a Professional Bachelor's Degree in Economics and IT. For my bachelor's thesis, I developed an enterprise architecture strategy for EnviroProcess Denmark and its parent company, EnviroProcess AB. This strategy was designed to align IT initiatives with the subsidiary’s core competencies, specific service knowledge, unique industry insights, and overall project execution.}
\newcommand{\finalContinuedLearning}{I am committed to continuously enhancing my skills and am currently exploring areas such as knowledge engineering, decision intelligence, and multi agent learning frameworks. Additionally, I am open to learning what is necessary for the company and specific role.}
\newcommand{\finalThankYou}{Thank you for your time. I look forward to the chance to discuss how my background and ambitions align with the goals of Aarhus Kommune. I am enthusiastic about potentially contributing to your projects and would appreciate the opportunity to discuss this further over a coffee.}
